Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh \emph{hp}-FEM

### 2010-10-27 results.tex
Some changes

An example of the solution at $t=0.7\ s$ and $t=3.0\ s$ 
calculated with the HP\_ANISO refinement mode is shown
in Figs.~\ref{fig:cphi-1} and \ref{fig:cphi-2}.

\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=.75\columnwidth]{cphi-1}
  \caption{\label{fig:cphi-1} Concentration $C$
  and voltage $\phi$ at $t=0.7\ s$.}
  \end{centering}
\end{figure}

@@

\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=.75\columnwidth]{cphi-2}
  \caption{\label{fig:cphi-2} Concentration $C$
  and voltage $\phi$ at $t=3.0\ s$.}
  \end{centering}
\end{figure}

@@

Comparison of single mesh H\_ANISO with p=1, single mesh H\_ANISO with p=2
and single mesh HP\_ANISO should be added here to make the point that 
hp-FEM is much better than low-order FEM. 
Otherwise the reader does not know 
why we are just using hp-FEM in the following. Or is there a reason 
why you do not want to add this here --  long computing time for hp-FEM or something 
else?

@@

\subsection{More general results}
\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=.75\columnwidth]{cphiorders}
  \caption{\label{fig:cphi-orders} Solutions $C$ and $\phi$
  and corresponding polynomial degrees of the elements at
  $t=0.7\ s$. HP\_ANISO refinement mode was used. The height
  in the solution graphs indicates the value.}
  \end{centering}
\end{figure}

>>>>

An example of the solution at $t=0.7\ s$ and $t=3.0\ s$ 
calculated with the HP\_ANISO refinement mode is shown
in Figs.~\ref{fig:cphi-1}~and~\ref{fig:cphi-2}.

\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=\columnwidth]{cphi-1}
  \caption{\label{fig:cphi-1} Concentration $C$
  and voltage $\phi$ at $t=0.7\ s$.}
  \end{centering}
\end{figure}

@@

\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=\columnwidth]{cphi-2}
  \caption{\label{fig:cphi-2} Concentration $C$
  and voltage $\phi$ at $t=3.0\ s$.}
  \end{centering}
\end{figure}

@@

First of all, the low-order FEM and $hp$-FEM were compared.
Comparison of single mesh H\_ANISO with p=1, single mesh H\_ANISO with p=2
and single mesh HP\_ANISO should be added here to make the point that 
hp-FEM is much better than low-order FEM. 
Otherwise the reader does not know 
why we are just using hp-FEM in the following. Or is there a reason 
why you do not want to add this here --  long computing time for hp-FEM or something 
else?

@@

\subsection{HP\_ANISO adaptivity with non-uniform boundary conditions}
\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=.75\columnwidth]{cphiorders}
  \caption{\label{fig:cphi-orders} Solutions $C$ and $\phi$
  and corresponding polynomial degrees of the elements at
  $t=0.7\ s$. HP\_ANISO refinement mode was used. The height
  in the solution graphs indicates the value.}
  \end{centering}
\end{figure}
